Learning \strips\ action models from {\em state-invariants}

### 2019-02-05 doc/ijcai-19-deductivelearning/deductivelearning.tex
first version sections 1 and 2 ijcai19 paper on deductive learning

The specification of a planning action model is a complex process that limits, too often, the potential of model-based planning systems~\cite{kambhampati:modellite:AAAI2007}. The {\em machine learning} of action models can relieve this {\em knowledge acquisition bottleneck} of {\em AI planning} and nowadays, there exists a wide range of effective approaches for learning planning action models~\cite{arora:amodels:ker2018}. Many of the most successful approaches for learning planning action models are however purely {\em inductive}~\cite{yang2007learning,pasula2007learning,mourao2010learning,zhuo2013action}, meaning that their success depends on the {\em amount} and {\em quality} of the input observations of plan executions.

This paper proposes the exploitation of {\em deductive} knowledge in the form of {\em state-invariants} (i.e logic formulae that specify constraints about the possible states of a given domain) to reduce the negative effects of insufficient input observations when learning action models. Our approach is built on top of the {\em classical planning} compilation for the learning of \strips\ action models~\cite{aineto2018learning}. This compilation approach is flexible to different kinds of input knowledge (e.g., partially/fully observations of actions of plan executions as well as partially/fully observed intermediate states) and guarantees to output an action model that is {\em consistent} with the input knowledge. In this paper we show that, in unfavorable scenarios where input observations are minimal (just an {\em initial state} and the {\em goals}), {\em state-invariant} help to learn better \strips\ models with the {\em classical planning} compilation.

>>>>

The specification of a planning action model is a complex process that limits, too often, the application of model-based planning to real-world tasks~\cite{kambhampati:modellite:AAAI2007}. The {\em machine learning} of action models can relieve this {\em knowledge acquisition bottleneck} of {\em AI planning} and nowadays, there exists a wide range of effective approaches for learning planning action models~\cite{arora:amodels:ker2018}. Many of the most successful approaches for learning planning action models are however purely {\em inductive}~\cite{yang2007learning,pasula2007learning,mourao2010learning,zhuo2013action}, meaning that their performance depends on the {\em amount} and {\em quality} of the input examples (namely observations of plan executions generated with the aimed action model).

This paper proposes the exploitation of {\em deductive} knowledge in the form of {\em state-invariants} (i.e logic formulae that specify constraints about the possible states of a given domain) to reduce the negative effects of insufficient input observations when learning \strips\ action models. Given an action model state-of-the-art planners use to compute {\em state-invariants} to reduce their search space and make the planning process more efficient~\cite{helmert2009concise}. In this paper we follow the oposite direction and exploit {\em state-invariants} to learn a planning action model.

Our approach is built on top of the {\em classical planning} compilation for the learning of \strips\ action models~\cite{aineto2018learning}. This compilation is flexible to different kinds of input knowledge (e.g., partially/fully observations of actions of plan executions as well as partially/fully observed intermediate states) and outputs an action model that is {\em consistent} with the given input knowledge. In this paper we show that, in unfavorable scenarios where input observations are minimal (just an {\em initial state} and the {\em goals}), {\em state-invariant} help to learn better \strips\ models with the {\em classical planning} compilation.
